Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-04 paper.tex
refactor abstract

We observe that in most cases, Linux kernel memory management scales well with
    large amounts of physical memory. However, workloads that allocated many
    virtual memory areas can accumulate significant memory and computational
    overhead due to kernel metadata.

In addition, transparent hugepages can induce significantly earlier
    onset of memory pressure in workloads that have random access patterns,
    which may nullify the benefits from better TLB behavior. This can happen
    even in workloads that would not otherwise experience memory pressure.
Finally, we see that the 99.99-th percentile of disk latency during swapping
    can account for over 70\% of runtime for the workloads we tested.

>>>>

We find that in most cases, Linux kernel memory management scales well with
    large amounts of physical memory. However, workloads that allocated many
    virtual memory areas can accumulate significant memory and computational
    overhead due to kernel metadata.     
    Furthermore, in certain situations, transparent hugepages can nullify the
    benefits from better TLB reaches by inducing memory pressure earlier, even
    for workloads that would otherwise not experience it.

Finally, we see that the 99.99-th percentile of disk latency during swapping
    can account for over 70\% of runtime for the workloads we tested.
